### 2016-12-17 Chapters/introduction.tex
Add space for french summary everywhere. Comment out chapter 2 abstract because chapter 3 has no abstract.
Finishing chapter 3, sent to Hidde and Hans

\section*{Summary}

This chapter presents... (approx. 1 page)

\selectlanguage{french}
\section*{Résumé}

Dans cette section... (env. 1 page)
\selectlanguage{english}

@@

\begin{figure}[!h]
\centering
\includegraphics[height=3cm]{./Fig/Chapter1/monod_law.eps}
\caption{Monod law, reproduced from~\cite{monod_growth_1949}.
Monod has been a pioneer in the formalization of microbial growth into fundamental coarse-grained relationships.
This figure shows the growth rate (in number of divisions per hour) of \textit{Escherichia coli} in a synthetic minimal medium at 37$^{\circ}$C containing different concentrations of glucose (a common carbon source).
As the concentration of glucose increases, the growth rate of \textit{E. coli} does so by following a hyperbolic relationship described in Eq~\ref{eq:monod_law}.
Solid line is drawn with $\mu_K = 1.35$ div.h\textsuperscript{-1}, and $K_C = 0.22 \cdot 10^{-4}$ mol.L\textsuperscript{-1}.
}
\label{fig:monod_law}
\end{figure}

@@

\begin{figure}[!h]
\centering
\includegraphics[height=6cm]{./Fig/Chapter1/scott_rnaprot.eps}
\caption{The growth law of ribosomal abundance (figure reproduced from Fig~S1 in~\cite{scott_interdependence_2010}).
For different carbon sources more or less rich, the RNA/protein ratio is linearly correlated with the growth rate, a relation that holds for many species of microorganisms.
This ratio is correlated with the fraction of ribosome-affiliated proteins, and therefore with the relative abundance of ribosomes in the cell.
}
\label{fig:scott_rnaprot}
\end{figure}

@@

\begin{figure}[!h]
\centering
\includegraphics[height=5cm]{./Fig/Chapter1/molenaar_overflow.eps}
\caption{The strategy of overflow metabolism, reproduced from~\cite{molenaar_shifts_2009}.
When increasing the concentration of substrate, the metabolism of microorganisms switches toward the use of inefficient pathways.
This paradoxical behavior does in fact maximize the growth rate if we take into account the costs and benefits of enzyme synthesis, in particular the fact that pathways for inefficient catabolism are shorter and therefore cheaper to produce.
(A) Simple view of microbial metabolism, with the two competitive efficient and inefficient pathways.
(B) The switching from efficient to inefficient catabolism when the concentration of nutrients, and hence the growth rate, increases.
}
\label{fig:molenaar_overflow}
\end{figure}

@@

\begin{figure}[!h]
\centering
\includegraphics[height=5cm]{./Fig/Chapter1/growth_curve.eps}
\caption{The different phases of a typical growth curve are visualized by the accumulation of biomass (black thick line) and the nutrient abundance in the medium (green dashed line).
(A) The lag phase, a variable period of time during which the organism adapt to the new medium.
It is hardly reproducible and strongly depends on the recent history of the culture.
(B) The steady-state (or balanced-growth) phase which is characterized by an exponential growth of biomass.
It presents constant and reproducible characteristics which has made it a standard for microbial growth studies~\cite{schaechter_microbe_2006}.
This phase can be extended for thousands of generations by the constant addition of fresh medium (continuous culture).
As represented here, nutrients are quickly depleted in batch conditions, which does not allow to maintain steady-state growth for a long period of time.
(C) The stationary phase, after the depletion of the limited nutrient in the medium.
In environmental conditions, microorganisms usually encounter poor media and spend most of their time in stationary phase.
Some species which have evolved long-term resistance mechanisms like sporulation can survive harsh conditions when in stationary phase.
}
\label{fig:growth_curve}
\end{figure}

>>>>

\selectlanguage{french}
\section*{Résumé en français}

Dans cette section... (env. 2 pages)
\selectlanguage{english}

@@

\begin{figure}[tb]
\centering
\includegraphics[height=5cm]{./Fig/Chapter1/monod_law.eps}
\caption{
\textbf{Monod law, reproduced from~\cite{monod_growth_1949}.}
Monod has been a pioneer in the formalization of microbial growth into fundamental coarse-grained relationships.
This figure shows the growth rate (in number of divisions per hour) of \textit{Escherichia coli} in a synthetic minimal medium at 37$^{\circ}$C containing different concentrations of glucose (a common carbon source).
As the concentration of glucose increases, the growth rate of \textit{E. coli} does so by following a hyperbolic relationship described in Eq~\ref{eq:monod_law}.
Solid line is drawn with $\mu_K = 1.35$ div.h\textsuperscript{-1}, and $K_C = 0.22 \cdot 10^{-4}$ mol.L\textsuperscript{-1}.
}
\label{fig:monod_law}
\end{figure}

@@

\begin{figure}[tb]
\centering
\includegraphics[height=7cm]{./Fig/Chapter1/scott_rnaprot.eps}
\caption{
\textbf{The growth law of ribosomal abundance (figure reproduced from Fig~S1 in~\cite{scott_interdependence_2010}).}
For different carbon sources more or less rich, the RNA/protein ratio is linearly correlated with the growth rate, a relation that holds for many species of microorganisms.
This ratio is correlated with the fraction of ribosome-affiliated proteins, and therefore with the relative abundance of ribosomes in the cell.
}
\label{fig:scott_rnaprot}
\end{figure}

@@

\begin{figure}[tb]
\centering
\includegraphics[width=\textwidth]{./Fig/Chapter1/molenaar_overflow.eps}
\caption{
\textbf{The strategy of overflow metabolism, reproduced from~\cite{molenaar_shifts_2009}.}
When increasing the concentration of substrate, the metabolism of microorganisms switches toward the use of inefficient pathways.
This paradoxical behavior does in fact maximize the growth rate if we take into account the costs and benefits of enzyme synthesis, in particular the fact that pathways for inefficient catabolism are shorter and therefore cheaper to produce.
(A) Simple view of microbial metabolism, with the two competitive efficient and inefficient pathways.
(B) The switching from efficient to inefficient catabolism when the concentration of nutrients, and hence the growth rate, increases.
}
\label{fig:molenaar_overflow}
\end{figure}

@@

\begin{figure}[tb]
\centering
\includegraphics[height=5cm]{./Fig/Chapter1/growth_curve.eps}
\caption{
\textbf{The different phases of a typical growth curve are visualized by the accumulation of biomass (black thick line) and the nutrient abundance in the medium (green dashed line).}
(A) The lag phase, a variable period of time during which the organism adapt to the new medium.
It is hardly reproducible and strongly depends on the recent history of the culture.
(B) The steady-state (or balanced-growth) phase which is characterized by an exponential growth of biomass.
It presents constant and reproducible characteristics which has made it a standard for microbial growth studies~\cite{schaechter_microbe_2006}.
This phase can be extended for thousands of generations by the constant addition of fresh medium (continuous culture).
As represented here, nutrients are quickly depleted in batch conditions, which does not allow to maintain steady-state growth for a long period of time.
(C) The stationary phase, after the depletion of the limited nutrient in the medium.
In environmental conditions, microorganisms usually encounter poor media and spend most of their time in stationary phase.
Some species which have evolved long-term resistance mechanisms like sporulation can survive harsh conditions when in stationary phase.
}
\label{fig:growth_curve}
\end{figure}
